### 2021-07-27 paper2/appendix.tex
Final version

\subsection{Transfer Learning}\label{sec:transfer-learning}
For our method, we require a representative set which follows the same distribution as that observed during deployment.
Such a representative set might not always be available.
In such a scenario, we can resort to using a set that is merely \emph{similar} to that in the deployment setting and leverage transfer learning.

@@

>>>>

@@

\subsection{Transfer Learning}\label{sec:transfer-learning}
\noindent For our method, we require a representative set which follows the same distribution as that observed during deployment.
Such a representative set might not always be available.
In such a scenario, we can resort to using a set that is merely \emph{similar} to that in the deployment setting and leverage transfer learning.

### 2021-07-27 paper3/paper3.tex
Finish
Final version

\chapter{Paper 3: Learning with Perfect Bags: Addressing Hidden Stratification with Zero Labelled Data}\label{ch:paper3}
%%%%%%%%% ICML 2021 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

@@

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Viktoriia Sharmanska$^1$, Myles Bartlett$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
% \textsc{Conference}:\;\; Submitted to \textit{International Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\; The appendix has been included as section~\ref{sec:zsf-appendix}.

>>>>

\chapter{Learning with Perfect Bags: Addressing Hidden Stratification with Zero Labelled Data}\label{ch:paper3}
%%%%%%%%% ICML 2021 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

@@

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:
Thomas Kehrenberg$^1$, Myles Bartlett$^1$, Novi Quadrianto$^1$ and Vik\-to\-riia Shar\-man\-s\-ka$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
% \textsc{Conference}:\;\; Submitted to \textit{International Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\; The appendix has been included as section~\ref{sec:zsf-appendix}.
